Behavior Driven Development in Haskell

### 2012-05-27 paper.tex
Add TBD for implementation of expectation combinators
Wording

%%%% Describe the problem.
\begin{quote}
    TBD: Important points we want to say about BDD:
    \begin{itemize}
        \item
            All behavior should be documented, together with some
            \emph{evidence} for that behavior.
        \item
            BDD approaches \emph{Test-driven development (TDD)} and
            \emph{Acceptance test-driven development (ATDD)} with a new
            terminology and mindset .  For the purpose of this paper we focus
            on the TDD aspect of BDD.
        \item
            Automating things, and continuous integration is an important
            aspect of BDD.
        \item
            BDD uses expectations instead of assertions
    \end{itemize}
\end{quote}

@@

>>>>

%%%% Describe the problem.
\begin{quote}
    TBD: Important points we want to say about BDD:
    \begin{itemize}
        \item
            All behavior should be documented, together with some
            \emph{evidence} for that behavior.
        \item
            \emph{Behavior driven development (BDD)} approaches
            \emph{test-driven development (TDD)} and \emph{acceptance
            test-driven development (ATDD)} with a new terminology and
            mindset.  For the purpose of this paper we only focus on
            the TDD aspect of BDD.
        \item
            Automating things, and continuous integration is an important
            aspect of BDD.
        \item
            BDD uses expectations instead of assertions
    \end{itemize}
\end{quote}

@@

\subsection{Combinators for expectations}

TBD: describe the implementation of {\tt shouldBe}, etc.
